En garde! Unguarded iteration for reversible computation in the Delay monad\thanks{Supported by organization x.}

### 2019-04-26 mpc19/paper.tex

  In this paper, we extend the two-level calculus of finitary \Pio{}
  to one for full \Pio{} (i.e., with both recursive types and
  iteration by means of a \trace{} combinator) using the \Delay{}
  monad, which can be regarded as a ``computability-aware'' analogue
  of the usual $\mathsf{Maybe}$ monad for partiality. This yields a
  calculus of iterative (and possibly nonterminating) reversible
  programs acting on user-defined dynamic data structures together
  with a calculus of certified program equivalences between these
  programs.

>>>>

In this paper, we extend the two-level calculus of finitary \Pio{} to one for
full \Pio{} (i.e., with both recursive types and iteration by means of a
\trace{} combinator) using the \Delay{} monad, which can be regarded as a
``computability-aware'' analogue of the usual $\mathsf{Maybe}$ monad for
partiality. This yields a calculus of iterative (and possibly non-terminating)
reversible programs acting on user-defined dynamic data structures together
with a calculus of certified program equivalences between these programs.
